IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-02 review/response_2.tex

		\begin{response}
			We agree with the reviewer that the signal model requires more description. The manuscript has been updated as follows.
			\begin{framed}
				As suggested in \cite{M-Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated waveform (deterministic multisine) to boost the spectrum and energy efficiency. The information signal transmitted over subband $n \in \mathcal{N} \triangleq \{1, \dots, N\}$ at time $t$ is
			\begin{equation}
				\boldsymbol{x}_{\mathrm{I},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
			\end{equation}
			where $\boldsymbol{w}_{\mathrm{I},n} \in \mathbb{C}^{M \times 1}$ is the information precoder at subband $n$, $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ is the information symbol at subband $n$, and $f_n$ is the frequency of subband $n$. On the other hand, the power signal transmitted over subband $n$ at time $t$ is
			\begin{equation}
				\boldsymbol{x}_{\mathrm{P},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
			\end{equation}
			where $\boldsymbol{w}_{\mathrm{P},n} \in \mathbb{C}^{M \times 1}$ is the power precoder at subband $n$. Therefore, the superposed signal transmitted over all subbands at time $t$ is
			\begin{equation}
				\boldsymbol{x}(t) = \Re{\left\{\sum_{n=1}^N(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
			\end{equation}
			\end{framed}
		\end{response}

		\begin{point}
			In Remark~\ref{M-re:subband_tradeoff}, the meaning of the sentence, ``there exists a tradeoff for auxiliary link control in the frequency domain'', is not clear to me.
		\end{point}

		\begin{response}
			By `auxiliary link control in the frequency domain', we intended to emphasize that the auxiliary link cannot be designed independently at different frequencies, and a resource allocation opportunity at the channel arises thanks to the IRS. The composite channel can be tuned flexibly to satisfy the specific requirement of the multi-carrier transmission. For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$). We have updated the Remark~\ref{M-re:subband_tradeoff} as follows.
			\begin{framed}
				The cascaded channel varies at different frequencies. Since we regard the reflection as frequency-flat, there exists a tradeoff for the passive beamforming design in the frequency domain. The composite channel can be tuned flexibly to satisfy the specific requirement of the multi-carrier transmission. For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$). This is essentially a resource allocation opportunity at the channel enabled by the IRS. In the MISO case, a similar effect also exists in the spatial domain. Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
			\end{framed}
			\label{re:2.10}
		\end{response}

@@

		\begin{point}
			Some editorial comments: 1) ``a (-->an) M-antenna''; 2) ``through a (-->an) L-element IRS''; 3) ``the CSIT of direct and cascaded channels are (-->is) known''; 4) ``It demonstrated (-->demonstrates) that''; 5) In Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}, the text in the y-axis is too long. Please divide it into two rows. Besides, the text in the x-axis of the upper figure is covered by the lower one.
		\end{point}

		\begin{response}
			We sincerely appreciate your careful reading and rigorous feedbacks. The manuscript have been revised accordingly and we will endeavor to avoid similar issues in the future.
		\end{response}
	\end{reviewer}

	\begin{reviewer}
		\begin{point}
			Proposition~\ref{M-pr:bcd} is questionable. The algorithm may not converge to a local optimal due to the coupling constraint~\eqref{M-co:original_rate}.
		\end{point}

		\begin{response}
			Thank you for pointing out this issue. Indeed, the local optimality is not guaranteed as \eqref{M-co:original_rate} couples all blocks together. We have removed the claim on optimality and updated Proposition~\ref{M-pr:bcd} as follows.
			\begin{framed}
				For any feasible initial point, the BCD Algorithm~\ref{M-al:bcd} is guaranteed to converge.
			\end{framed}
			The proof has been modified correspondingly.
			\begin{framed}
				The objective function \eqref{M-ob:original} is non-decreasing over the iterations, because the IRS phase shift by Algorithm~\ref{M-al:sca} is local optimal, the active precoder by \eqref{M-eq:b_n} is global optimal, and the waveform amplitude and splitting ratio by Algorithm~\ref{M-al:gp} are local optimal. \eqref{M-ob:original} is also upper-bounded due to the unit-modulus constraint \eqref{M-co:original_modulus} and the transmit power constraint \eqref{M-co:original_power}. Therefore, Algorithm~\ref{M-al:bcd} is guaranteed to converge. However, it may not converge to optimal points since variables are coupled in constraint~\eqref{M-co:original_rate} \cite{M-Grippo2000}.
			\end{framed}
			\label{re:3.1}
		\end{response}

@@

		\begin{point}
			The figures are too small. For example, Fig.~\ref{M-fi:scaling_reflector}, the axis legend is not fully shown.
		\end{point}

		\begin{response}
			We apologize for the inconvenience. The figures have been amplified and the legends have been calibrated.
		\end{response}

		\begin{point}
			It is said that the reference path loss is \SI{35}{\dB} at \SI{1}{\meter}, while for the center frequency at \SI{5.18}{\GHz}, even adopting the free space path loss model also will lead a much sever path loss at \SI{1}{\meter}. It is not clear how the authors calculate this.
			\label{pt:3.3}
		\end{point}

		\begin{response}
			We agree with the reviewer that the reference path loss used in the simulation is faulty and we sincerely apologize for this issue. The parameter \SI{35}{\dB} was considered in some IRS literatures without specifying the operating frequency, and it was taken in the previous simulations without careful consideration. In the corrected manuscript, we instead consider a center frequency at \SI{2.4}{\GHz} that corresponds to a free-space path loss of \SI{40}{\dB} at \SI{1}{\meter}. The path loss used in the simulation is taken from IEEE TGn channel model D \cite{M-Erceg2004} where the slope is set to \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and set to \num{3.5} onwards. This has a similar effect to most IRS literatures that assign a relatively large path loss exponent to the direct path and smaller ones to the incident and reflected paths to penalize the channel with large distance.

			In the updated manuscript, we raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi} to compensate the \SI{5}{\dB} difference and maintain the simulation results in the same level. Please refer to the following specification for details.
			\begin{framed}
				We consider a large open space Wi-Fi-like environment at \SI{2.4}{\GHz} center frequency where the channel is modeled by IEEE TGn channel model D \cite{M-Erceg2004}. Specifically, the path loss exponent is set to \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and set to \num{3.5} onwards. All fadings are modeled as Non-Line-of-Sight (NLoS) with tap delays and powers specified by model D. The tap gains are modeled as i.i.d. CSCG variables. Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$ \cite{M-Clerckx2016a}. We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (hence one-dimensional search to obtain the R-E region).
			\end{framed}
		\end{response}

@@

		\begin{point}
			The authors considered the practical reflection coefficient beamforming in the simulation results. It is not clear how the authors obtain the discrete phase shift results. Direct quantization method and some other customized optimization techniques for discrete phase shifts may have significant performance gap, see \cite{Wu2020c}. Also, this work adopts the same uniform quantization as the above work, which thus needs to be clarified in the paper.
		\end{point}

		\begin{response}
			Thank you for the clarification. The discrete phase shift is obtained by quantizing the continuous phase shift obtained by Algorithm~\ref{M-al:bcd} to the uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$. We are aware that quantization can lead to performance loss compared with direct optimization over feasible phase shift set. In the revised manuscript, we have emphasized this point as follows.
			\begin{framed}
				On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and perform quantization on the continuous reflection coefficients returned by Algorithm~\ref{M-al:bcd} to reduce the circuit complexity and control overhead\footnotemark.
			\end{framed}
			\footnotetext{Note that this relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS). The readers are referred to \cite{Wu2020c} for details.}
		\end{response}

@@

		\begin{point}
			There are also some other practical phase shift models and nonlinear energy harvesting models such as saturation model for IRS-aided SWIPT in existing works, which may be discussed as related works such as amplitude-dependent phase shift model.
		\end{point}

		\begin{response}
			We have added reference \cite{Xu2021} in the updated manuscript that models the saturation effect of energy harvesters and physical properties of the IRS. Its contributions have been summarized in the manuscript as follows.
			\begin{framed}
				In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage to reduce overall complexity. It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to practical IRS and harvester models.
			\end{framed}
		\end{response}

@@

		\begin{point}
			Some early magazine papers and recent tutorial papers related to IRS-aided WPT/WIT may be further discussed.
		\end{point}

		\begin{response}
			We have incorporated aforementioned references into the manuscript as follows.
			\begin{framed}
				\textellipsis The hardware architecture, design challenges and application opportunities of practical IRS are covered in \cite{Wu2020}.
